\papertitle

### 2012-10-13 manuscript.tex
some additions to conclusion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
We have demonstrated cooperative guidance of a 13 gram flapping wing MAV with a
lightweight base station in hardware. In addition, we developed a model of the
cooperative system by modeling the individual system capabilities, and composing
it with known system interactions. The corroboration between our simulated and
experimental results shows that our simplified modeling approach is useful for 
predicting the performance of cooperative systems.

We intend to further explore the benefits and limitations of collaboration in
unstructured environments by deploying our base station on millirobotic ground
vehicles. As the ground station used in this work was designed with this goal
in mind, this is a matter of implementation. The effectiveness of our modeling
approach, when applied to more complex systems with more interactions and 
agents is also an future area of interest.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
We have demonstrated cooperative guidance of a 13 gram flapping-wing MAV with a
lightweight base station in hardware. In addition, we developed a model of the
cooperative system using system identification methods on the individual system capabilities, and composing
it with known system interactions. The corroboration between our simulated and
experimental results shows that our simplified modeling approach is useful for 
predicting the performance of cooperative systems at low computational cost. Our model could also be used to determine when to begin control with high probability of success, even though we lack information about the complete pose of the MAV.

We intend to further explore the benefits and limitations of collaboration in
unstructured environments by deploying our base station on millirobotic ground
vehicles. As the ground station used in this work was designed with this goal
in mind, this is a matter of implementation. The effectiveness of our modeling
approach, when applied to more complex systems with more interactions and 
agents is also a future area of interest.
